Improving content discovery through combining linked data and data mining techniques

### 2016-05-06 report/chapters/04-implementation.tex
Tables seem fine now

def generate(g, subject=None, depth=3, features=None, prefix=''):
    if depth <= 0:
        return
    if not features:
        features = {}
    if not subject:
        subject = g.identifier
    for p, o in g.predicate_objects(subject=subject):
        if type(o) == URIRef:
            new_prefix = prefix + clean(p) + '_'
            features[new_prefix + clean(o)] = True
            generate(g, depth=(depth - 1), features=features, prefix=new_prefix, subject=o)
        elif type(o) == Literal:
            features[clean(p)] = str(o)

>>>>

def generate(
    g, subject=None, depth=3, features=None, prefix=''
    ):
    if depth <= 0:
        return
    if not features:
        features = {}
    if not subject:
        subject = g.identifier
    for p, o in g.predicate_objects(subject=subject):
        if type(o) == URIRef:
            new_prefix = prefix + clean(p) + '_'
            features[new_prefix + clean(o)] = True
            generate(
                g,
                depth=(depth - 1),
                features=features,
                prefix=new_prefix,
                subject=o)
        elif type(o) == Literal:
            features[clean(p)] = str(o)

### 2016-05-06 report/chapters/05-analysis.tex
Tables seem fine now

\begin{table}[h]
  \centering
  \caption{Number of clusters produced by each combination of approaches}
  \label{tbl:cluster-counts}
  \begin{tabular}{lll}
    & Not enriched & Enriched \\
    Deference                                     & 5            & 249      \\
    Entity Extraction                             & 35           & 32       \\
    Hyperlink Relationships                       & 2            & 56       \\
    Dereference and Entity Extraction             & 329          & 340      \\
    Entity Extraction and Hyperlink Relationships & 199          & 233      \\
    Dereference and Hyperlink Relationships       & 53           & 117      \\
    All three extractions                         & 184          & 223     
  \end{tabular}
\end{table}

@@

@@

\begin{sidewaystable}[p]
  \centering
  \begin{tabular}{|l|l|l|}
    $N=2$                                 & $N=9$                                                   & $N=265$                                     \\
    \hline
    ogp:image="[\ldots]"                  & rdf:type\_schema:RadioEpisode=true                      & md:item\_rdf:nil=true                       \\
    foaf:topic\_dbpedia:BBC\_iPlayer=true & schema:url="[\ldots]"                                   & foaf:topic\_dbpedia:Digg                    \\
    rdf:type\_schema:RadioEpisode=true    & foaf:topic\_dbpedia:JavaScript                          & twitter:card:"summary\_large\_image"        \\
    rdfa:usesVocabulary\_schema=true      & meta:twitter:card="summary"                             & foaf:topic\_dbpedia:LinkedIn                \\
    meta:twitter:card="summary"           & foaf:topic\_dbpedia:Listen\_(Beyonc\'e\_Knowles\_song)" & meta:apple-mobile-web-app-title="BBC Sport" \\
  \end{tabular}
  \caption{Ten most common features across the smallest, the largest and a mean-sized cluster produced by the enriched union of dereference and entity extraction}
  \label{tbl:top-features-3-1}
\end{sidewaystable}

>>>>

@@

\begin{table}[h]
  \centering
  \begin{tabular}{|l|ll|}
    \hline
     & Not enriched & Enriched \\
    \hline
    Deference                                     & 5            & 249      \\
    Entity Extraction                             & 35           & 32       \\
    Hyperlink Relationships                       & 2            & 56       \\
    Dereference and Entity Extraction             & 329          & 340      \\
    Entity Extraction and Hyperlink Relationships & 199          & 233      \\
    Dereference and Hyperlink Relationships       & 53           & 117      \\
    All three extractions                         & 184          & 223     \\
    \hline
  \end{tabular}
  \caption{Number of clusters produced by each combination of approaches}
  \label{tbl:cluster-counts}
\end{table}

@@

\begin{sidewaystable}[p]
  \centering
  \renewcommand{\arraystretch}{1.5}
  \begin{tabular}{|l|l|l|}
    $N=2$                                 & $N=9$                                                   & $N=265$                                     \\
    \hline
    ogp:image="[\ldots]"                  & rdf:type\_schema:RadioEpisode=true                      & md:item\_rdf:nil=true                       \\
    foaf:topic\_dbpedia:BBC\_iPlayer=true & schema:url="[\ldots]"                                   & foaf:topic\_dbpedia:Digg                    \\
    rdf:type\_schema:RadioEpisode=true    & foaf:topic\_dbpedia:JavaScript                          & twitter:card:"summary\_large\_image"        \\
    rdfa:usesVocabulary\_schema=true      & meta:twitter:card="summary"                             & foaf:topic\_dbpedia:LinkedIn                \\
    meta:twitter:card="summary"           & foaf:topic\_dbpedia:Listen\_(Beyonc\'e\_Knowles\_song)" & meta:apple-mobile-web-app-title="BBC Sport" \\
  \end{tabular}
  \caption{Ten most common features across the smallest, the largest and a mean-sized cluster produced by the enriched union of dereference and entity extraction}
  \label{tbl:top-features-3-1}
\end{sidewaystable}

### 2016-05-06 report/chapters/06-evaluation.tex
Fixed broken references
Tables seem fine now

A higher-level
goal of this research was to perform some more qualitative evaluation
of those clusters by obtaining human feedback on a potential
application thereof. The application evaluated was a feature that would
take a page a user is currently reading and suggest related content
based on their being members of the same cluster. Mock-ups of such
a feature were generated and evaluated via a survey as described
in section~\ref{sec:survery}.

@@

\begin{table}[h]
  \centering
  \caption{Success rate for each pipeline variant in generating related content suggestions}
  \label{tbl:results}
  \begin{tabular}{lll}
    & Not enriched & Enriched \\
    Deference                                     & 5\%          & 44\%     \\
    Entity Extraction                             & 17\%         & 37\%     \\
    Hyperlink Relationships                       & 8\%          & 14\%     \\
    Dereference and Entity Extraction             & 34\%         & 37\%     \\
    Entity Extraction and Hyperlink Relationships & 16\%         & 11\%     \\
    Dereference and Hyperlink Relationships       & 26\%         & 30\%     \\
    All three extractions                         & 23\%         & 24\%     
  \end{tabular}
\end{table}

>>>>

A higher-level
goal of this research was to perform some more qualitative evaluation
of those clusters by obtaining human feedback on a potential
application thereof. The application evaluated was a feature that would
take a page a user is currently reading and suggest related content
based on their being members of the same cluster. Mock-ups of such
a feature were generated and evaluated via a survey as described
in section~\ref{sec:survey}.

@@

\begin{table}[h]
  \centering
  \caption{Success rate for each pipeline variant in generating related content suggestions}
  \label{tbl:results}
  \begin{tabular}{|l|ll|}
  \hline
    & Not enriched & Enriched \\
    \hline
    Deference                                     & 5\%          & 44\%     \\
    Entity Extraction                             & 17\%         & 37\%     \\
    Hyperlink Relationships                       & 8\%          & 14\%     \\
    Dereference and Entity Extraction             & 34\%         & 37\%     \\
    Entity Extraction and Hyperlink Relationships & 16\%         & 11\%     \\
    Dereference and Hyperlink Relationships       & 26\%         & 30\%     \\
    All three extractions                         & 23\%         & 24\%     \\
\hline
  \end{tabular}
\end{table}
